### 2017-11-07 Docs/Thesis/docs/chapter5.tex
updates on thesis text

As proof of concepts for our tool, we are going to use Mininet's emulated testbeds. These tests are easily implemented and reproduced, and are able to test the performance on traffic generation realism. Tests in a physical testbeds of, and network functions stays for future work.

This first testbed is a tree topology, and represents tests performed by Swing\cite{swing-paper} found on the literature \cite{background-traffic-matter}\cite{legotg-paper}. The second is much simples, and is just a one hop connection of two hosts. Both topologies are SDN neworks, and have OpenDayLight Beryllium as controller.

All the traffic is generated by the host \textit{h1} with IPv4 address 10.0.0.1. The traffic will to be captured form the host interface with TCPdump in a pcap format, and just the outgoing traffic will be considered. Any response packet form the hosts will be ignorated, since we want to evaluate just the traffic generated by the host, as it were a replay engine, such as TCPreplay or TCPivo\cite{tcpivo-paper}

@@

All scripts used to create the scenarios, automate the tests, and cae the traffic, and the Octave scripts to perfom all thelable at the poject github repository\footnote{\href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}}. They are organized as a set of python packages to enable easy reproductionon Github\footnote{\textcolor{red}{github-link}}. To start rub and with all depencies installed, you should not take more than 10 minutes.

We will perform this testes using SIMITAR \textit{alpha} version, operation as a client on host \textit{h1}, and as a server on all other hosts. As traffic generator engine, we will use Iperf, D-ITG, and Libtins C++ API.

@@

\section{Simitar using D-ITG with skype-pcap}

@@

\section{Simitar lanDiurnal-pcap/bigFlows-pcap}

\subsection{Iperf as packetgen tool}

\subsection{Libtins as packetgen tool}

>>>>

As proof of concepts for our tool, we are going to use Mininet's emulated testbeds. We automate these tests using scripts, so they are reproducible.  They are responsible for building the topology, run the SIMITAR traffic generator, collect \textit{pcaps} and perform the proposed proof of concept analysis.  We make four plots for each trace, where we compare the original and the synthetic trace. The first two we used just for visual comparison:  flows per second and bandwidth. To compare the quality of the realism of the generated traffic, we plot the Flows cumulative distribution function\cite{harpoon-paper}, and the Wavelet multiresolution analysis\cite{swing-paper}.  Tests on physical testbeds and network functions stay for future work.

\begin{table}[ht!]
	\centering
	\caption{Experiments specification table}
	\label{tab:specifications}
	\begin{tabular}{ll}
		\hline
		Processor            & Intel(R) Core(TM) i7-4770, 8 cores, CPU @ 3.40GHz \\
		RAM                  & 15.5 GB                                           \\
		HD                   & 1000 GB                                            \\
		Linux         & 4.8.0-59-generic                                  \\
		Ubuntu        & Ubuntu 16.10 (yakkety)                            \\
		SIMITAR       & v0.4.2 (Eulemur rubriventer)                      \\
		Mininet       & 2.3.0d1                                           \\
		Iperf         & iperf version 2.0.9 (1 June 2016) pthreads        \\
		Libtins       & 3.4-2                                             \\
		OpenDayLight v & 0.4.0-Beryllium                                   \\
		Octave        & 4.0.3                                             \\
		Pyshark              & 0.3.6.2                                           \\
		Wireshark            & 2.2.6+g32dac6a-2ubuntu0.16.10                     \\ \hline
	\end{tabular}
\end{table}

We use two different testbeds: a tree topology (figure~\ref{fig:topo-tree}), similar to tests performed by Swing\cite{swing-paper}\cite{background-traffic-matter}\cite{legotg-paper}, and a single hop connection of two hosts. Both topologies are SDN networks and have OpenDayLight Beryllium as the controller.  We present the complete specification of these experiments at the table ~\ref{tab:specifications}.

We generate the traffic on the host \textit{h1} with IPv4 address 10.0.0.1. The traffic is captured from the host interface with TCPdump in a \textit{pcap} format.  We organized the project directory tree as follows\footnote{ \href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests} }: we placed the software at \texttt{SIMITAR}. We paced the validation tests, with short tutorials at \texttt{Tests} directory. The software documentation is at \texttt{Docs} directory. We organized the tests as python packages, configurable by a \texttt{config.py} file.

@@

@@

@@

\section{Current Limitations}
